Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-09 paper.tex
Created a subsection for the evaluation measures

After this process, several forecasting techniques have been tested, such as rule- or tree-based, together with numerical methods. 
% Antonio - is 'numerical' the best term for these kind of methods?
%FERGU: OJO que en esta sección a veces usáis el presente perfecto (have been) y otras el presente (is performed)
% Antonio - Corregido. ;)
%
The obtained results have been compared and analysed, computing, in addition to the obtained \textit{correlation coefficient}, some error measures from the literature \cite{ChingChin2010,Madsen2008}. We have considered the widely accepted standard formulae \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011} or R \cite{otexts,Hyndman2013}.
Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
%FERGU: have been selected for this methodology, for this work... algo así
% Antonio - ya se ha dicho. ;)

@@

>>>>

After this process, several forecasting techniques have been tested, such as rule- or tree-based, together with numerical methods. 
% Antonio - is 'numerical' the best term for these kind of methods?
%FERGU: OJO que en esta sección a veces usáis el presente perfecto (have been) y otras el presente (is performed)
% Antonio - Corregido. ;)
%

@@

\subsection{Models evaluation}

At this step, the developed forecasting models are evaluated and assessed based on different evaluation criteria. In addition to the \textit{correlation coefficient}, we have considered the widely accepted standard formulae in the literature \cite{gepsoft} (Equations \ref{eq:MAE} to \ref{eq:RRSE}), which are implemented in tools like Weka \cite{pentaho,Witten2011} or R \cite{otexts,Hyndman2013}.
Specifically, in order to compute the forecasting errors of the different methods, Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute error (RAE) and Root relative squared error (RRSE) have been selected:
%FERGU: have been selected for this methodology, for this work... algo así
% Antonio - ya se ha dicho. ;)
